A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 4_method.tex
lil improvements
move source files to top level hierarchy

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
\caption{Layer outline}\label{overview_outline}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
\caption{Skeleton}\label{overview_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
\caption{Union of cones}\label{overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
\caption{Slicing}\label{overview_uniform_sliced}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
\caption{Uniform paths}\label{overview_uniform_paths}
\end{subfigure}

\setlength{\figwidth}{.22\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
\caption{Center identification}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/quantized.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
\caption{Quantization}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_magenta.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
\caption{Smoothing}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
The first row illustrates the generation of uniform paths \subref{overview_uniform_paths}
by interpreting the path as the intersection between horizontal planes and the union of cones \subref{overview_uoc}, which is an alternative visualization of the skeleton \subref{overview_skeleton}. 
The second row depicts the stages with both 2D and 3D visualizations for generating paths with adaptive width \subref{3d_surface_overview_sliced}.
Central elements in the skeleton are first identified (blue in \subref{3d_surface_overview_center}).
The heights are then quantized in terms of number of beads (the integer values in \subref{3d_surface_overview_rounded}), and smoothed \subref{3d_surface_overview_smoothed}.
}
\label{3d_surface_overview}
\end{figure*}

For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
These terms will be further explained as they first appear later in this paper.

\begin{figure}\centering
\includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
\label{legend}
\end{figure}

@@

\begin{figure}\centering
\setlength{\figwidth}{0.24\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoidation}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
}
\label{skeletonization_comparison}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.3\columnwidth}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=\figheight,frame]{sources/method/naive_overfill_underfill.pdf}
\caption{Over- and underfill}\label{naive_overfill_underfill}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.8\figheight]{sources/method/significance_properties.pdf}
\caption{Significance measure}\label{distance_based_angles}
\end{subfigure}
\caption{
Properties of the significance measure along a skeletal edge (red) generated from two polygon lines (black) using the properties of inscribed circles (gray) and their radii (dashed).
\subref{naive_overfill_underfill}
The size of overfill (orange) and underfill areas (azure) for the uniform toolpathing technique can be calculated from the bisector angle.
% $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
\subref{distance_based_angles}
The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
}
\end{figure}

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.pdf}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/wedge_no_transitioning.png}
\caption{Without transitioning}
\end{subfigure}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/wedge_transitioning.png}
\caption{Transitioning}
\end{subfigure}
\caption{
Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
}
\label{transitions}
\end{figure}

@@

\begin{figure}\centering
\setlength{\figheight}{.2\columnwidth}
\begin{subfigure}{.55\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/peripheral_heights_3D.png}
\caption{Surface mesh}
\end{subfigure}
\begin{subfigure}{.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/peripheral_heights.pdf}
\caption{ST}
\end{subfigure}
\caption{
Shallow corners will cause peripheral nodes for which the height should be determined based on the central node above it.
}
\label{peripheral_heights}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation_beading.pdf}
\caption{Example beadings}\label{example_beading}
\end{subfigure}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation.pdf}
\caption{Interpolation}
\end{subfigure}
\caption{
Interpolation between two beadings $B^1$ and $B^2$ with odd and even bead count resulting in a beading $B^x$ at $n+\nicefrac23$.
Bead indices are counted inward from the outline (thick black).
Interpolation of locations in dots, interpolation of widths in dashes.
}
\label{beading_interpolation}
\end{figure}

\begin{figure}\centering
\setlength{\figheight}{.2\columnwidth}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_3D.png}
\includegraphics[height=\figheight]{sources/method/beading_conflict.pdf}
\caption{Beading conflict}\label{beading_conflict}
\end{subfigure}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_solved_3D.png}
\includegraphics[height=\figheight]{sources/method/beading_conflict_solved.pdf}
\caption{Conflict resolution}\label{beading_conflict_solved}
\end{subfigure}
\caption{
\subref{beading_conflict} The beading propagated from above conflicts with the beading below.
\subref{beading_conflict_solved} The beading conflict is resolved by gradually interpolating between the two beadings.
The ramp to the upper ridge doesn't line up with the lower ridge, which means that
the toolpaths (dashed) resulting from the beading propagated from above doesn't align with the beading from the thin outline feature (highlighted in red).
}
\label{beading_conflict_problem}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings to generate sites along trapezoids.
\subref{trapezoid_beading_beading} shows the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
No sites will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{site_placement}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.3\columnwidth}
\begin{subfigure}{.5\columnwidth}\centering
\includegraphics[width=\figheight,rotate=90]{sources/method/domains.pdf}
\caption{Polygon domains}\label{shape_decomposition_domains}
\end{subfigure}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/segment_generation.pdf}
\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Generating toolpaths on a part of the test outline shape by chaining together extrusion segments along each polygon domain.
Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figwidth}{.35\columnwidth}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_before}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_after}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overfill.
Toolpath locations in black, underfill in azure and overfill in orange.
}
\label{polyline_reduction}
\end{figure}

>>>>

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-input.pdf}
\caption{Layer outline}\label{overview_outline}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-uoc.pdf}
\caption{Skeleton}\label{overview_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-UoC-with-cones.png}
\caption{Union of cones}\label{overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-naive-cropped.png}
\caption{Slicing}\label{overview_uniform_sliced}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-naive.png}
\caption{Uniform paths}\label{overview_uniform_paths}
\end{subfigure}

\setlength{\figwidth}{.22\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-marking-cropped.png}

@@

\includegraphics[width=\figheight]{sources-method-overview-2D-marked.pdf}
\caption{Center identification}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-quantized.png}

@@

\includegraphics[width=\figheight]{sources-method-overview-2D-rounded.pdf}
\caption{Quantization}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-smoothed-magenta.png}

@@

\includegraphics[width=\figheight]{sources-method-overview-2D-smoothed.pdf}
\caption{Smoothing}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-cropped.png}

@@

\includegraphics[width=\figheight]{sources-method-overview-2D-sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
The first row illustrates the generation of uniform paths \subref{overview_uniform_paths}
by interpreting the path as the intersection between horizontal planes and the union of cones \subref{overview_uoc}, which is an alternative visualization of the skeleton \subref{overview_skeleton}. 
The second row depicts the stages with both 2D and 3D visualizations for generating paths with adaptive width \subref{3d_surface_overview_sliced}.
Central elements in the skeleton are first identified (blue in \subref{3d_surface_overview_center}).
The heights are then quantized in terms of number of beads (the integer values in \subref{3d_surface_overview_rounded}), and smoothed \subref{3d_surface_overview_smoothed}.
}
\label{3d_surface_overview}
\end{figure*}

For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
These terms will be further explained as they first appear throughout this paper.

\begin{figure}\centering
\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
\label{legend}
\end{figure}

@@

\begin{figure}\centering
\setlength{\figwidth}{0.24\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-st}
\caption{Skeletal Trapezoidation}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources-method-half-edge-datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
}
\label{skeletonization_comparison}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.3\columnwidth}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=\figheight,frame]{sources-method-naive-overfill-underfill.pdf}
\caption{Over- and underfill}\label{naive_overfill_underfill}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.8\figheight]{sources-method-significance-properties.pdf}
\caption{Significance measure}\label{distance_based_angles}
\end{subfigure}
\caption{
Properties of the significance measure along a skeletal edge (red) generated from two polygon lines (black) using the properties of inscribed circles (gray) and their radii (dashed).
\subref{naive_overfill_underfill}
The size of overfill (orange) and underfill areas (azure) for the uniform toolpathing technique can be calculated from the bisector angle.
% $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
\subref{distance_based_angles}
The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
}
\end{figure}

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.13\textwidth}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--bead-count.pdf}
\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-ends.pdf}
\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{\figwidth}
\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transitions-applied.pdf}
\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\begin{subfigure}{.27\textwidth}
\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-transitioning-filtering--result-uoc.pdf}
\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}

@@

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning.png}
\caption{Without transitioning}
\end{subfigure}
\begin{subfigure}{0.9\figwidth}\centering
\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning.png}
\caption{Transitioning}
\end{subfigure}
\caption{
Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
}
\label{transitions}
\end{figure}

@@

\begin{figure}\centering
\setlength{\figheight}{.2\columnwidth}
\begin{subfigure}{.55\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-peripheral-heights-3D.png}
\caption{Surface mesh}
\end{subfigure}
\begin{subfigure}{.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-peripheral-heights.pdf}
\caption{ST}
\end{subfigure}
\caption{
Shallow corners will cause peripheral nodes for which the height should be determined based on the central node above it.
}
\label{peripheral_heights}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-trapezoid-beading-interpolation-beading.pdf}
\caption{Example beadings}\label{example_beading}
\end{subfigure}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-trapezoid-beading-interpolation.pdf}
\caption{Interpolation}
\end{subfigure}
\caption{
Interpolation between two beadings $B^1$ and $B^2$ with odd and even bead count resulting in a beading $B^x$ at $n+\nicefrac23$.
Bead indices are counted inward from the outline (thick black).
Interpolation of locations in dots, interpolation of widths in dashes.
}
\label{beading_interpolation}
\end{figure}

\begin{figure}\centering
\setlength{\figheight}{.2\columnwidth}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-3D.png}
\includegraphics[height=\figheight]{sources-method-beading-conflict.pdf}
\caption{Beading conflict}\label{beading_conflict}
\end{subfigure}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-solved-3D.png}
\includegraphics[height=\figheight]{sources-method-beading-conflict-solved.pdf}
\caption{Conflict resolution}\label{beading_conflict_solved}
\end{subfigure}
\caption{
\subref{beading_conflict} The beading propagated from above conflicts with the beading below.
\subref{beading_conflict_solved} The beading conflict is resolved by gradually interpolating between the two beadings.
The ramp to the upper ridge doesn't line up with the lower ridge, which means that
the toolpaths (dashed) resulting from the beading propagated from above doesn't align with the beading from the thin outline feature (highlighted in red).
}
\label{beading_conflict_problem}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-trapezoid-beading-beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-trapezoid-beading-propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-trapezoid-beading-separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings to generate sites along trapezoids.
\subref{trapezoid_beading_beading} shows the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
No sites will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{site_placement}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.3\columnwidth}
\begin{subfigure}{.5\columnwidth}\centering
\includegraphics[width=\figheight,rotate=90]{sources-method-domains.pdf}
\caption{Polygon domains}\label{shape_decomposition_domains}
\end{subfigure}
\begin{subfigure}{.45\columnwidth}\centering
\includegraphics[height=\figheight]{sources-method-segment-generation.pdf}
\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Generating toolpaths on a part of the test outline shape by chaining together extrusion segments along each polygon domain.
Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
By following the trapezoids along the domain (cyan) of a single outline polygon,
the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
}
\label{segment_generation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figwidth}{.35\columnwidth}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth,frame]{sources-method-polyline-reduction-before}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth,frame]{sources-method-polyline-reduction-after}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overfill.
Toolpath locations in black, underfill in azure and overfill in orange.
}
\label{polyline_reduction}
\end{figure}

### 2019-08-30 5_generalization.tex
move source files to top level hierarchy

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth,frame]{sources/method/transition_length_limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources/validation/widths_legend_small.pdf}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth,frame]{sources-method-transition-length-limit.pdf}
\caption{
Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
}
\label{transition_placement}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}
